On Secure Delegation of SampBQP with a Classical Client

### 2020-02-05 preliminaries.tex
Add original proj lemma

We use the projection lemma from \cite{kempe_kitaev_regev_2006}, which projects the ground state of the Hamiltonian $H_1$ to the ground space of a Hamiltonian $H_2$ with a large gap.

\hannote{original text?}
\begin{thm}
	Let $H_1, H_2$ be local Hamiltonians where $H_2\geq0$. Let $K=\ker H_2$.
	$$\exists J=\frac{\poly(\norm{H_1})}{\lambda(H_2|_{K^\bot})}$$
	$$\lambda(H_1+JH_2)\geq\lambda(H_1\big|_K)-\frac{1}{8}$$
\end{thm}

@@

We also use the quantum full homomorphic encryption (QFHE) scheme given in \cite{mahadev_qfhe} which allows the use of a classical client.

\begin{dfn}
	A homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
	\begin{itemize}
		\item $\mathsf{HE.Keygen}(1^\lambda, 1^L)\rightarrow(pk, evk, sk)$
		\item $\mathsf{HE.Enc}_{pk}(\mu)\rightarrow c$
		\item $\mathsf{HE.Dec}_{sk}(c)\rightarrow \mu^*$
		\item $\mathsf{HE.Eval}_{evk}(f, c_1, \ldots, c_l)\rightarrow c_f$
	\end{itemize}
\end{dfn}

@@

\begin{thm}
	\label{decodeMeasureOrder}
	There exists a QFHE $\mathsf{QHE}=(\mathsf{QHE.Keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$ with the following extra properties:
	\begin{itemize}
		\item $\mathsf{QHE.Keygen}$ can be done classically.
		\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
		\item \Ethan{Is this obvious from the construction or do we need proof here?} Let $\Lambda$ be a product of $X$ and $Z$ measurements. Then there exists $\Lambda'$ product of $X$ and $Z$ measurements and $\widehat{\mathsf{QHE.Dec}}$ a BPP algorithm so that
			$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
	\end{itemize}
\end{thm}

@@

\begin{dfn}
	Let $\lambda$ be a security parameter.
	Let $(\bbP, \bbV)$ be an interactive protocol with security parameter $\lambda$.
	Then it is IND-CPA secure if $\forall x\in\set{0,1}^n$ no polynomial time adversary $\cA$ can win \myprotoref{protoIndCPA} with probability better than $\frac{1}{2}+\negl(\lambda)$
\end{dfn}

\begin{protocol}{$\QPIP_1$ protocol for $\SampBQP$}
	\label{ProtoIndCPA}
	\begin{enumerate}
		\item The challenge picks $b\in\set{0,1}$ at random
		\item If $b=0$, the challenger runs the protocol with the adversary, acting as the verifier with input $0^n$
		\item Otherwise, the challenger runs the protocol with the adversary, acting as the verifier with input $x$
		\item $\cA$ attempts to guess $b$
	\end{enumerate}
\end{protocol}

>>>>

We use the projection lemma from \cite{kempe_kitaev_regev_2006}, which relates the ground state of Hamiltonians $H_1 + H_2$ with the ground state of $H_1\big|_{\ker H_2}$.

\begin{thm}
	Let $H=H_1+H_2$ be the sum of two Hamiltonians operating on some Hilbert space $\cH=\cS+\cS^\bot$.
	The Hamiltonian $H_2$ is such that $\cS$ is a zero eigenspace and the eigenvectors in $\cS^\bot$ have eigenvalues at least $J>2\norm{H_1}$. Then,
	$$\lambda\left(H_1\big|_\cS\right)-\frac{\norm{H_1}^2}{J-2\norm{H_1}^2}\leq\lambda(H)\leq\lambda\left(H_1\big|_\cS\right)$$
\end{thm}

We will instead use the following formulation, which can be obtained by relabeling variables from above.

\begin{thm}
	\label{thm:projection}
	Let $H_1, H_2$ be local Hamiltonians where $H_2\geq0$. Let $K=\ker H_2$. Then,
	$$\exists J=\frac{\poly(\norm{H_1})}{\lambda\left(H_2\big|_{K^\bot}\right)}$$
	$$\lambda(H_1+JH_2)\geq\lambda\left(H_1\big|_K\right)-\frac{1}{8}$$
\end{thm}

@@

We also use the quantum fully homomorphic encryption scheme given in \cite{mahadev_qfhe} which is compatible with our use of a classical client.

\begin{dfn}
	A leveled homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
	\begin{itemize}
		\item $\mathsf{HE.Keygen}(1^\lambda, 1^L)\rightarrow(pk, evk, sk)$
		\item $\mathsf{HE.Enc}_{pk}(\mu)\rightarrow c$
		\item $\mathsf{HE.Dec}_{sk}(c)\rightarrow \mu^*$
		\item $\mathsf{HE.Eval}_{evk}(f, c_1, \ldots, c_l)\rightarrow c_f$
	\end{itemize}
\end{dfn}

@@

\begin{thm}
	\label{decodeMeasureOrder}
	There exists a QFHE $\mathsf{QHE}=(\mathsf{QHE.Keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$ with the following extra properties:
	\begin{itemize}
		\item $\mathsf{QHE.Keygen}$ can be done classically.
		\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
		\item \Ethan{Is this obvious from the construction or do we need proof here?} Let $\Lambda$ be a product of $X$ and $Z$ measurements. Then there exists $\Lambda'$ product of $X$ and $Z$ measurements and $\widehat{\mathsf{QHE.Dec}}$ so that
			$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
	\end{itemize}
\end{thm}

@@

\begin{dfn}
	Let $\lambda$ be a security parameter.
	Let $(\bbP, \bbV)$ be an interactive protocol with security parameter $\lambda$.
	Then it is IND-CPA secure if $\forall x\in\set{0,1}^n$ no polynomial time adversary $\cA$ can win \protoref{indcpa} with probability better than $\frac{1}{2}+\negl(\lambda)$
\end{dfn}

\begin{protocol}{$\QPIP_1$ protocol for $\SampBQP$}
	\label{proto:indcpa}
	\begin{enumerate}
		\item The challenge picks $b\in\set{0,1}$ at random
		\item If $b=0$, the challenger runs the protocol with the adversary, acting as the verifier with input $0^n$
		\item Otherwise, the challenger runs the protocol with the adversary, acting as the verifier with input $x$
		\item $\cA$ attempts to guess $b$
	\end{enumerate}
\end{protocol}
